Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-29 intro.tex
arch file

We develop these ideas in an Iris-based\mytodo{cite JFP} separation logic, and verify simplified versions of several critical virtual-memory-related pieces of OS functionality, including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory.

>>>>

\begin{figure}
   \includegraphics[width=0.5\columnwidth]{architecture.png}
  \caption{Layers of Implementation}
  \label{fig:architecture}
  \end{figure}
We develop these ideas in an Iris-based\mytodo{cite JFP} separation logic, and verify simplified versions of several critical virtual-memory-related pieces of OS functionality, including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory.
